pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-01-24 article.tex
Finish first draft of introduction

Diversification models are getting more complex over time. There are many
reasons for this. One reason is the increase in computing power,
allowing this heightened complexity to be possible.
Another reason is to explore a process that is not
yet captured by the other diversification models. An example of this
is the multiple-birth model [Laudanno, Bilderbeek & Etienne, in preparation], 
that is the first model to allow speciation to co-occur.

>>>>

Diversification models are getting more complex over time. There are many
reasons for this. One reason is the increase in computing power,
which allows this heightened complexity possible.
Another reason is to explore a process that is not
yet captured by the other diversification models. An example of this
is the multiple-birth model [Laudanno, Bilderbeek & Etienne, in preparation], 
that is the first model to allow speciation to co-occur.

An open question for each new diversification model is if the increased
complexity is worth the extra computational resources. There are many
ways to answer this question. One possible experiment 
is to use a phylogeny of the new diversification model,
simulate its alignment and see how well our
current inference models are at retrieving the phylogeny.
If this difference is small enough, current models apparently
suffice.

\verb;pirouette; is an R package that performs such an experiment,
and is built on \verb;babette; [Bilderbeek & Etienne, 2018], 
which calls the popular Bayesian inference tool 
BEAST2 [X and Bouckaert et al., ????]. With \verb;pirouette;, one
can easily measure the error made by Bayesian inference in recovering
any given phylogeny, helping us to valorize new diversification models.
